```{r}
source("setup.R")
```

```{r}
data("knz_bison")
```

1.  Create a new column in the bison dataset that calculates the individual's age at the time of observation.
```{r}
knz_bison <- knz_bison %>%
  mutate(obsage = rec_year - animal_yob)
```

2. Write a function that will first filter the bison dataset based on any user-specified weight threshold (returning the filtered dataset).
```{r}
bison_weight_filter <- function(weight) {
  knz_bison %>%
    filter(animal_weight > weight)
}

weight_threshold = 500

bison_weight_filter(weight_threshold)
```

```{r}
light_bison <- bison_weight_filter(300)  # Bison weighing more than 300 units
heavy_bison <- bison_weight_filter(700)  # Bison weighing more than 700 units
```

3.  Create a boxplot showing weight distribution between male and female bison, and then conduct a t-test to see if weight is significantly difference between males and females.
```{r}
# Create boxplot
knz_bison %>% 
  ggplot() +
  geom_boxplot(aes(x = animal_sex, y = animal_weight)) +
  labs(x = "Sex", y = "Weight", title = "Weight Distribution by Sex in Bison")

# The boxplot shows that it seems to be unequal variance in weights between male and female, so we use Levene test to prove
knz_bison %>% 
  levene_test(animal_weight ~ animal_sex)

# Perform Welch's t-test (assuming unequal variances)
knz_bison %>% 
  t_test(animal_weight ~ animal_sex, var.equal = FALSE, detailed = TRUE)

```

